\documentclass{article}
\title{\textit{it's vic!} Terms of Service for Freelance and Contract Work}
\author{Victor B. DBA \textit{it's vic!}}
\date{\textit{Last edited} December 12, 2023 (Draft)}
\begin{document}

\maketitle
\tableofcontents

\renewcommand{\labelenumi}{\alph{enumi})}

\section{Introduction}
Thank you for choosing to work with \textit{it's vic!}. The following terms and conditions (\textbf{''the Terms''}) outline the legal agreement between you (\textbf{''the Client''}) and Victor B. (\textbf{\textit{''it's vic!''}}, \textbf{''We''}, \textbf{''Us''}, \textbf{''Our''}) for the provision of freelance and contract services (\textbf{''the Services''}). Our Services cover 
\begin{enumerate}
    \item development of frontend or backend applications such as, but not limited to, web services, web applications, desktop applications and mobile applications;
    \item User Interface and User Experience design of a frontend application such as, but not limited to, web applications, desktop applications and mobile applications;
\end{enumerate}
which will be referred to as \textbf{''the Work''}.

\subsection{Changes to the Terms}
We reserve the right to modify and update these Terms at any time. The Client will be notified of any changes, and continued use of the services shall constitute acceptance of the updated Terms. Notification of changes may occur over the communication medium in use between Us and the Client, or on Our website. It is also the Client's responsibility to review these Terms periodically.

\subsection{Agreement to the Terms}
By using our Services, the Client agrees with the Terms as outlined in this document, and affirms that they are either
\begin{enumerate}
    \item at least 18 years of age, or;
    \item if under the age of 18, that they have obtained verifiable consent from a parent or legal guardian to use our services.
\end{enumerate}
If the Client is under 13 years of age, they are prohibited from using the Services. We reserve the right to request proof of age or guardian consent at any time.

\section{Payment}
The Services are paid for on an hourly rate chosen freely by Us. The rate is not bound by these Terms, and is instead decided by Us for a given Client depending on the type of work being done as a part of the Services.

We will give a price estimate to the Client based on the rate and expected time complexity. Before any work can start as a part of the Services, the Client must pay 50\% of this price estimate as a one-time fee. The fee will be subtracted from the invoice total.

The price estimate is provided for reference. The total price will depend on hours spent on the Work.

\subsection{Payment Terms and Collection Procedures}
The Client has 30 days to pay for a completed Work from the moment of the creation of the associated invoice for the Work. If the Client does not pay within 30 days, We may request a third-party to collect the payment, along with any late fees, on Our behalf.

\subsection{Refunds and Cancellation}
We do not offer refunds for the one-time fee or the final invoice for the Work, as the Work is in a purely digital form and does not have a physical counterpart of any kind.

If the Client wishes to cancel their order, the Client will have to pay for any extra hours not covered by the one-time fee, if any. After the cancellation, the Client wiil not receive the unfinished Work, and We will retain the ownership to the work.

\section{Provision of the Services}
\subsection{Deadlines}
We reserve the right to complete a Work within a minimum of 30 days starting from the payment of the one-time fee, or more if the Work will take more time than expected due to:
\begin{enumerate}
    \item health issues;
    \item time management issues; % here only bc of school
    \item and any other issues that may arise.
\end{enumerate}
Both parties acknowledge that unforeseeable events beyond reasonable control (force majeure) may impede timely completion of the Work. Such events may include, but are not limited to, acts of nature, war, government actions, or any other unforeseen circumstances beyond reasonable control.

If We believe that the Work will take longer than the anticipated minimum of 30 days, the Client will be notified as soon as possible. Both parties are able to negotiate the appropriate time extension.

\subsection{Ownership of the Work}
The Work is owned solely by Us until the Client has paid for the completed Work. The Client agrees to not use the Work in any way, shape or form, such as but not limited to:
\begin{enumerate}
    \item promotional material;
    \item announcements;
    \item providing services with the Work;
    \item and any other uses not mentioned here,
\end{enumerate}
until the completed Work is paid for.

The Client agrees, unless explicitly stated otherwise, that We may include the Client in Our promotional material for our Services after the completion of the Work.

\subsection{Support and Warranty}
We are not obligated to provide support after the completion of the Work. We do not provide any kind of warranty for the completed Work. The Client may seek extra support services from Us on a case-by-case basis.

\section{Privacy and Confidentiality}
\subsection{Compilance with Laws and Regulations}
We are committed to complying with the General Data Protection Regulation in accordance with local Polish laws, and by extension European Union laws.

We regularly work with third-party service providers such as Stripe, Inc. (\textbf{''the Third Parties''}). We are not responsible for any violations of the California Consumer Privacy Act or other such local laws and regulations that may be committed by the Third Parties.

\subsection{Confidentiality}
We shall not disclose, divulge, or share any information provided by the Client, including but not limited to,
\begin{enumerate}
    \item business strategies;
    \item proprietary data;
    \item trade secrets;
    \item or any other confidential material owned by the Client,
\end{enumerate}
without the explicit written consent of the Client.

\end{document}
